Baking the Perfect Cookie

### 2022-12-06 paper.Rmd
small change

---
title: "Baking the Perfect Cookie"
subtitle: "STT 863 Fall 2022"
author: "Benjamin Agyei, Christian Miller, Elliot Shannon, Grayson White"
date: '2022-12-07'
output: pdf_document
bibliography: references.bib
nocite: '@*'
fontsize: 12pt
geometry: margin=1in
spacing: double
fig_caption: yes
indent: true
---

>>>>

---
title: "Baking the Perfect Cookie"
subtitle: "STT 863 Fall 2022"
author: "Benjamin Kwadwo Agyei, Christian Miller, Elliot Shannon, Grayson White"
date: '2022-12-07'
output: pdf_document
bibliography: references.bib
nocite: '@*'
fontsize: 12pt
geometry: margin=1in
spacing: double
fig_caption: yes
indent: true
---
